---
title: DANL Project
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Name Meghan Catania
  - Name Abby Dunnigan
  - Name Emily Peters
  - Name Teddy Packert
  - Name Collin Gates

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)
install.packages("dplyr")
library(dplyr)
install.packages("ggplot2")
library(ggplot2)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

About this project :clap:

```{r}
athletes <- read_csv('/Users/meghancatania/Downloads/Most_paid_athletes.csv')
athletes <- read_csv('/Users/meghancatania/Downloads/Most_paid_athletes.csv')
```


# Data

The data.frame `mpg` contains a subset of the fuel economy data that the EPA makes available on [https://fueleconomy.gov/](https://fueleconomy.gov/). It contains only models which had a new release every year between 1999 and 2008 - this was used as a proxy for the popularity of the car. :oncoming_automobile:


## Summary Statistics

```{r}

```

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(athletes) 
```


```{r}
skim(athletes) %>% 
  select(-n_missing)
```


## MPG and a Type of Cars
The following graph shows how the distribution of salary of athletes ('earnings ($ millions)') varies by a type of sport (`sport`) :football: :soccer: .


```{r}
sport_earning <- athletes %>%
  select(Sport,`Current Rank`)
top_sport <- sport_earning %>%
  group_by(variable.names('American Football',Soccer,Basktetball,Golf))
sport_graph <- top_sport %>%
 filter(Sport %in% c('American Football','Soccer','Basketball','Golf'))

ggplot(sport_graph) +
  geom_point(aes(x = Sport, y = 'Current Rank'), alpha=.9) +
  scale_y_discrete(labels= c("label1","label2")) +
  labs(x = "Sport", y = "Current Rank") 
```


