---
title: DANL Project
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Name Meghan Catania
  - Name Abby Dunnigan
  - Name Emily Peters
  - Name Teddy Packert
  - Name Collin Gates

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

About this project :clap:

```{r}
athletes <- read_csv('/Users/meghancatania/Downloads/Most_paid_athletes.csv')
athletes <- read_csv('/Users/meghancatania/Downloads/Most_paid_athletes.csv')
```


# Data

The data.frame `mpg` contains a subset of the fuel economy data that the EPA makes available on [https://fueleconomy.gov/](https://fueleconomy.gov/). It contains only models which had a new release every year between 1999 and 2008 - this was used as a proxy for the popularity of the car. :oncoming_automobile:


## Summary Statistics

```{r}

```

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(athletes) 
```


```{r}
skim(athletes) %>% 
  select(-n_missing)
```


## MPG and a Type of Cars
The following graph shows how the distribution of salary of athletes ('earnings ($ millions)') varies by a type of sport (`sport`) :football:.


```{r}
ggplot(data = mpg) +
  geom_boxplot(aes(x = class, y = hwy, fill = class),
               show.legend = F) +
  labs(x = "Class", y = "Highway\nMPG") 
```


